%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{NauvalPanca}{Atmaja}
       {Software Engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
  	Jl Komarudin No. 15
  	Kp Pisangan, RT 03/RW 05,
  	Penggilingan, Cakung
  	Jakarta Timur,
  	DKI Jakarta, 13940
  	Indonesia
    ~
    +62 858 5391 5000
    ~
    \href{https://www.linkedin.com/in/nauvalatmaja/}{linkedin.com/in/nauvalatmaja}
    \href{mailto:nauval.atmaja@gmail.com}{nauval.atmaja@gmail.com}
    \href{https://github.com/npatmaja}{github.com/npatmaja}
    \href{http://nauvalatmaja.com}{nauvalatmaja.com}
  \section{languages}
  	Bahasa Indonesia
  	English
  \section{programming}
    {\color{red} $\varheartsuit$} Java
	JavaScript (node.js), C\#, PHP, Go
    CSS3 \& HTML5
\end{aside}

\section{interests}

Software engineering, software architecture, domain-driven design, event-drivent architecture,
design patterns, software testing, functional programming, devops, information architecture,
user experience.

\section{experience}

\begin{entrylist}
  \entry
    {04/18-Now}
    {Advotics, Jakarta}
    {Software Development Manager}
    {My responsibilities are shifted to be more involved in building teams,
	defining and refining product development processes, communicating concerns or clarifications to stakeholders,
	and designing/reviewing/improving overall system architecture. Initiating CI/CD pipelines, mentoring team members
	(including introduction to TDD and event-sourcing architecture using Java and Kafka),
	having regular one-on-one session with team members are part of what I have been doing for the role.\\
	In this role, I report directly to CTO and coordinate with product team.}
  \entry
    {08/17-04/18}
    {Advotics, Jakarta}
    {Senior Software Development Engineer}
    {Lead software development teams to deliver new features and new products and their operation in production.
	This includes (but not limited to) designing and developing backend services, code reviewing, deploying and solving operation issues.
	We used several widely used technologies such as Java with Spring Boot framework, MySQL, Vue.js and AWS cloud services.\\
	In this position, I directly report to CTO}
  \entry
    {11/15 - 07/17}
    {Tripvisto, Jakarta}
    {Senior Software Engineer}
	{Developed Tripvisto's platform (\emph{tripvisto.com}), including its back-end services and its back-office system.
	We used some popular technologies such as node.js, react, redux, elasticsearch, redis, laravel, nginx, git, etc.}
  \entry
	{02/15 - 11/15}
	{Gushcloud, Jakarta}
	{Senior Web Developer}
	{Developed a platform to manage Gushcloud's campaign cycle from proposal to its execution. The platform
	is built using node.js, express.js and MongoDB stack.}
  \entry
	{03/14 - 07/14}
	{LORIA, Nancy}
	{Intern}
	{Joined PAREO team and actively involved in development of a property-based testing framework for Tom/Gom
	and eventually Java programs. The outcome of the internship was a property-based testing framework built based
	on JUnit, which also served as my dissertation project at Erasmus Mundus DESEM program.}
  \entry
	{12/09 - 08/12}
	{McDermott Indonesia, Batam}
	{Application Developer}
	{Involved in a various IT project initiatives. The activities ranged from gathering requirements, designing and implementating the solutions
	and maintaining them in producition.}
  % \entry
	% {12/08 - 12/09}
	% {PT. CBC, Jakarta}
	% {Application Engineer}
	% {Implementation of IFS (ERP software) at Kawasaki Motor Indonesia}
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
	{2012 - 2014}
	{Erasmus Mundus M.Sc. on Dependable Software Systems}
	{University of St. Andrews (Scotland), Universit\'{e} de Lorraine (France)}
	{A double degree program funded by European Union that focuses on the aspects
	of dependable software systems development.\\
	Theses:\\
	\emph{Visualisation Tool for Grasp ADL (2013)}\\
	\emph{Property-based testing (2014)}}
  \entry
	{2004 - 2008}
	{B.Sc. in Information System}
	{Sepuluh Nopember Institute of Technology (ITS), Surabaya}
	{Majoring in information system\\
	Specialization in decission support system}
\end{entrylist}
\end{document}
